### 2018-10-25 inst/table_tennis_serve.Rmd
change docs to match actual scores used

* A vs B, A serves, 5-1
* A vs B, B serves, 1-3
* A vs C, A serves, 5-1
* A vs C, C serves, 1-3

@@

and the likelihood ratio
```{r}
LR <- exp(delta_support)
LR
```

>>>>

* A vs B, A serves, 5-1
* A vs B, B serves, 1-3
* A vs C, A serves, 4-1
* A vs C, C serves, 1-2

@@

and the likelihood ratio is:
```{r}
LR <- exp(delta_support)
LR
```
